### 2016-11-28 ms/ms.tex
make new resilence figs

\begin{abstract}  
 % The ability of communities to maintain function in the face of
  %species extinction is related to the structure of networks. Lauren - i changed the phrasing because structure of network and network structure were too close.
  The structure of interaction networks is related to the ability of communities to maintain function in the face of
  species extinction. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for conservation
  biology. Using a nine-year-dataset comprising nearly $20,000$
  pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing community assembly to be
  punctuated by major interaction reorganizations.%  In contrast, the
  % non-assembling networks did not restructure as frequently.
  % Across all communities, pollinator species were opportunistic in the
  % flowers they visited.
   Generalist species were the most persistent and 
also the most variable in their network positions, contrary to
  what is expected through prefereantial attachment theory. % High
  % species and interaction turnover was ubiquitous across assembling
  % and non-assembling communities, though unique interactions turned
  % over at higher rates in assembling hedgerows as the networks
  % continually reorganized.
  % Nestedness of assembling networks also increased through time, but
  The sensitivity of networks to cascading perturbations,
  increased with assembly, at least partially due to accumulating
  species richness. We elucidate some of the mechanisms underlying
  plant-pollinator network assembly and restoration --- challenging
  the widely-held hypothesis that mutualistic networks assemble
  through preferential attachment.
\end{abstract}

@@

%% there are other ways to assemble that are not preferentia;
%% attchment, particularly vis big reorganizations of interactions
%% Lauren I love this paragraph!
In contrast to the network build-up described by preferential
attachment, significant reorganizations of interactions can punctuate
assembly \citep{peel2014detecting}. Such significant reorganizations
of interactions, or network changing points, are observed in social
networks that respond to abrupt shifts in the behavior of interactors
\citep{peel2014detecting}. In ecological communities, such shifts may
occur if, as new species colonize, resident species change their
interaction partners to optimize their foraging effort. In
plant-pollinator communities, theory predicts that pollinators
optimize their use of floral resources to reduce interspecific
competition and improve resource-use efficiency
\citep{pyke1984optimal, valdovinos2010consequences,
  valdovinos2013adaptive, albrecht2010plant, Bluthgen2007}. No
studies, however, have examined whether network changing points occur
during ecological network assembly, and how these changes relate to
the species behavior.

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially ``applied succession''
\citep[e.g.,][]{parker1997scale}. In pollination systems, the time
since an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, devoto2012understanding}, suggesting
interactions are changing as the community develops. Understanding the
mechanisms of network assembly will help to guide community
restoration. Facilitating network restoration is especially imperative
in areas where species interactions provide essential ecosystem
services, such as crop pollination. To ensure the continued provision
of ecosystem services and curb biodiversity loss, it is critical to
restore pollinators and their interactions in agricultural
landscapes. To promote pollinator services in agriculture, farmers may
chose to plant strips of native plants along farm edges (hedgerows) to
help provide habitat for pollinators without removing arable land from
production. Hedgerows augment the richness, abundance and trait
diversity of pollinators in agricultural landscapes
\citep{morandin-2013-829, kremen-2015-602, ponisio2015farm}, and
promote the persistence and colonization of floral resource
specialists \citep{mgonigle-2015-x}. It is important to understand how
these new species are being incorporated into the network as the
community assembles, and the consequences for interaction patterns and
robustness.

%% Lauren I would put 10 year dataset; and I *loved* the way you
%% organized the ideas here!!
We explore the process of network development using a nine year
dataset of plant-pollinator community assembly following hedgerow
restoration in the highly simplified and intensively managed
agricultural landscape of California's Central Valley.  We first
determine whether the mechanism underlying network assembly is a build
up of interactions as would be predicted by preferential attachment,
or instead is punctuated by significant reorganizations of
interactions (i.e., network changing points). Even with changing
points in interaction organization, networks could still be assembling
via preferential attachment if the network reorganizations were
primarily driven by peripheral, temporally variable species while a
stable, well-connected core of species persist. We test whether the
species that are most variable in their network position --- and thus
important contributors to network reorganizations --- are less
persistent and connected species. To further explore the mechanisms
underlying the temporal dynamics of the networks, we examine patterns
in the species and interaction temporal turnover. Lastly, we
investigate whether networks are assembling toward predictable
interaction patterns, and the ramifications for the robustness of the
networks to species extinction and cascading perturbations.

%% objectives
% 1) Are hedgerows assembling by preferential attachment, or are there
% more abrupt reorganizations of network structure?
% 2) Who are the species responsible for interaction reorganizations?
% how to incorporate this? 
% 3) Are the changing points a product of turnover in species
% composition, or are more substantial changes in the verticles of the
% networks?
% 4) Is the structure of interactions changing? Does this change the
% robustness of the network to species extinction and/or perturbation?

\section*{Materials \& Methods}
\label{sec:methods}

\subsection*{Study sites and collection methods}
\label{sec:study-sites}

We surveyed plant-pollinator interaction networks of independent
assembling hedgerows communities (N=5), and of two types of
non-assembling communities to serve as controls: unrestored, weedy
field margins (N=19) and mature hedgerows (greater than 10 years since
planting, N=29). The sites were located in the Central Valley of
California in Yolo, Colusa and Solano Counties. This area is composed
of intensively managed agriculture --- primarily monocultures of
conventional row crops, vineyards and orchards. Hedgerows are ca.~3--6
m wide and approximately 350 m long, bordering large (ca.\
30--hectare) crop fields. Hedgerows consist of native, perennial,
shrub and tree plantings including \textit{Rosa californica},
\textit{Cercis occidentalis}, \textit{Ceanothus spp.},
\textit{Heteromeles arbutifolia}, \textit{Sambucus mexicana},
\textit{Eriogonum spp.}, \textit{Baccharis spp.}, \textit{Salvia
  spp}. and others \citep[Fig.~S1][]{menz-2010-4, kremen-2015-602,
  mgonigle-2015-x}. The mean distance between monitoring sites was
$15$ km, and the minimum distance between sites sampled in the same
year was 1 km.  The entire area surveyed spanned almost $300$
km$^2$. The crop fields adjacent to all sites were similarly managed
as intensive, high-input monoculture.

Monitoring of assembling hedgerows began in 2006 and continued through
2014. Surveys of these sites began the year before the area was
restored. For logistical reasons, no sampling of assembling hedgerows
was conducted in 2010. Sites were sampled between two and five times
per year (Tables S1-S3, mean $3.4$ samples per year). In each round of
sampling, the order in which sites were sampled was
randomized. Surveys were conducted under sunny conditions when the
temperature was above $21^{\circ}\mathrm{C}$ and wind speed was below
$2.5$ meters/second.

Flower-visitors to plants in hedgerows and unrestored controls were
netted for one hour of active search time (the timer was paused when
handling specimens). Honeybees (\textit{Apis mellifera}) were not
collected because their abundance is determined largely by hive
placement by bee-keepers. All other insect flower visitors that
touched the reproductive parts of the flower were collected; however,
here we focus only on wild bees and syrphids --- the most abundant and
effective pollinators in the system (representing 49 and 19 percent of
records, respectively, C.~Kremen, A.~Klein and L.~Morandin,
unpublished data). Bee and syrphid specimens were identified to
species (or morpho-species for some bee specimens in the genera
\textit{Nomada} and \textit{Sphecodes}) by expert taxonomists.

Quantitative networks were generated for each site through time. To
account for the unequal number of surveys between years (Tables
S1-S3), we use the mean of the interactions between a pair of plants
and pollinators across surveys within a year to represent interaction
frequency.

\subsection*{Change point analysis}
\subsubsection*{Identifying change points}
We employed a change point detection method \citep{peel2014detecting}
to identify fundamental reorganizations in large-scale interaction
patterns. A change point is caused by a merge, split, fragmentation or
formation of modules (also called compartments). Change point
detection methods have yet to be generalized to quantitative networks,
so for this analysis we focused on qualitative (binary)
networks. Following \cite{peel2014detecting}, we first defined a
probability distribution over the networks using the generalized
hierarchical random graph model (GHRG). The GHRG model is able to
capture both assortative and disassortative structure patterns at all
scales in the network \citep{peel2014detecting}. A network $G$ is
composed of vertices $V$ and edges $E$. The GHRG model decomposes the
$N$ vertices into a series of nested groups, the relationships among
which are represented by the dendrogram $T$. The tips of $T$ are the
vertices of $G$, and the probability that two vertices $u$ and $v$
connect is given by the parameter $p_r$. The probability distribution
of the network $G$ is thus defined as:

\begin{equation}
  \label{eq:lik}
  P(G|T,{pr}) = p_r^{E_r}(1-p_r)^{N_r-E_r}
\end{equation}
% 
Where $E_r$ is the observed number of edges between vertices with the
common ancestor $r$, and $N_r$ is the total possible edges.

Using Bayesian posterior inference and techniques from phylogenetic
tree reconstruction, we fit the GHRG model to the networks
\citep{peel2014detecting}. This is accomplished by using a Markov
chain Monte Carlo (MCMC) procedure to first sample the posterior
distribution of bipartitions, from which a consensus tree is derived
\citep{peel2014detecting}. We use $\beta$ distributions with the
hyperparameters $\alpha=\beta=1$ to define priors for $p_r$.

Once the GHRG model has been fit to the networks, we determine whether
a change point occurred between two time slices. To detect a change
point, we use Bayes factors to compare the fit of two models --- one
where a change point occurred between two networks, and one where no
change occurred. We chose a sliding window of length, $w$, of four,
within which to find change points. Larger windows allow for more
gradual changes, and four was the maximum possible with our eight
years of data. Lastly, to calculate a $p$-value for the Bayes factors,
we use parametric bootstrapping to numerically estimate the null
distribution \citep{peel2014detecting}. We employed code published
online by L.~Peel for the change point analysis. Analyses were
conducted in Python 3.4.

We next test whether the change points occurring in maturing hedgerows
were a component of the assembly process or a product of environmental
shifts that lead to network reorganizations in all types of
communities. We model the number of change points as successes and the
total number of years each site was sampled as trials, and use a
generalized linear model with Binomial error to test whether the
probability of a change point occurring varied by site type
\citep{lme4}. We used standard techniques to determine whether the
assumptions of the models were met for this and all subsequent
models. For the non-assembling hedgerows and weedy field margins, only
sites with five or greater survey years were included in this analysis
(N=11). All statistical analyses were conducted in R 3.2.3 \citep{R}.

To further elucidate the nature of the change points, we examine the
characteristics of the species that contributed to interaction
reorganization. Some species remain in relatively similar network
positions through time, whereas others are more variable in their
position and thus contribute more strongly to network
reorganization. We test whether the more persistent species with the
highest degree (number of different interaction partners) are the
most stable in their network positions, as would be expected if the
networks were assembling via preferential attachment.

We calculate species persistence as the proportion of surveys in which
a plant or pollinator is observed. Species observed consistently
within and between years are thus maximally persistent. Weighted
species degree is calculated from interaction observations from an
extensive dataset from Yolo County (approx.~18000 interaction records)
that included both the data included in this study and additional data
from sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness centrality \citep{freeman1978centrality} at each
site through time. Closeness centrality represents the importance of a
space by calcuating the path lengths to other vertices (species) in
the network \citep{freeman1978centrality}. The shorter the mean path
length to other species, the higher the closeness centrality. We use
linear mixed models to test whether the species closeness variability
(log) is related to the persistence or degree of that species
\citep{lme4, lmetest}. We included random effects for species and
site. Because the degree and persistence of pollinators were strongly
correlated, ($\rho = 0.071$, $p$-value $<$ $2*10^{-16}$), we include
each explanatory variable in separate models. Plant degree and
persistence were not significantly correlated, but we use the same
models as we did for the pollinators for consistency.  Because an
approximately logarithmic increase in closeness centrality, as would
be expected with assembly by preferential attachment, would also lead
to high variability in closeness scores, we also test whether log
closeness centrality increases through time.

\subsection*{Species and interaction turnover}

%%Lauren I really liked the way you explained this part =]
Reorganizations of network structure can be the result of species
turnover or species changing their interaction partners (i.e.,
re-wiring). To better understand the mechanisms underlying the
temporal dynamics of the assembling networks, we examined patterns of
species and interaction turnover. For example, assembling networks may
have higher rates of pollinator turnover than non-assembling
communities because new pollinator species are colonizing and
establishing themselves \citep{mgonigle-2015-x}. Similarly, because
species are turning over and pollinators are trying to maximize their
foraging efficiency based on the species present, interactions may
turnover more quickly than in established communities. In addition, at
assembling hedgerows, plants that are unvisited in early years may
appear to ``colonize'' the networks as they became more attractive
resources and establish new interactions with pollinators.

@@

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, occupying the same network position and interacting with
similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species (Fig.~
S2). We develop a method to examine the temporal turnover of
interactions with weightings based on their similarity. We followed
the algorithm of \cite{ahn2010link} to cluster all the interactions
(edges) hierarchically across sites and years based on their
similarity, and build a dendrogram. The interaction similarity is
based how may plants and pollinators (vertices) two edges share
\citep{ahn2010link, kalinka2011linkcomm}. The more species edges
shared in common, the shorter the branch length between them on the
dendrogram.  We next calculated the temporal turnover of interactions
weighted by their similarity, as approximated by ``phylogenetic''
distance \citep{graham2008phylogenetic, picante-2010-1463}. We then
use linear mixed models to test whether the weighted turnover of
interactions varied between assembling and non-assembling networks,
including site as a random effect \citep{lme4, lmetest}.

@@

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
%Network nestedness significantly increased with assembly
%(Fig.~\ref{fig:baci}, estimate of the slope of nestedness through time
%$\pm$ SE, $1.834 \pm 0.6142$, $p$-value=$0.022$). 
Nestedness and modularity did not change in any predictable pattern with assembly (Fig.~\ref{fig:baci}). All of the networks were significantly nested ($z$-scores $>$ 2), but not modular ($z$-scores $<$ 2, Fig.~\ref{fig:baci}).

@@

\subsection*{Network robustness}
Assembly did not affect network robustness to species
extinction when species were removed incrementally by
degree % (estimate
% of the slope of robustness through time $\pm$ SE, $6*10^{-5} \pm
% 4*10^{-3}$, $p$-value=$0.987$)
or abundance. % ($0.001 \pm 0.003$,
% $p$-value=$0.65$)
In contrast, the sensitivity of networks to cascading perturbations,
as measured by the algebraic connectivity of the network, increased as
the network assembled (Fig.~\ref{fig:rob}, estimate of the slope of
sensitivity to cascading perturbations through time $\pm$ SE, $0.6814
\pm 0.272$, $p$-value=$0.042$).

@@

We would like to thank Paulo R.~Guimar{\~a}es Jr., Aaron Clauset,
Matthew Hutchinson and Ana Paula A. Assis for their invaluable
discussions and comments, and Leto Peel for help with the change point
analysis.  We thank the growers and land owners that allowed us to
work on their property. We also greatly appreciate the identification
assistance of expert taxonomists Martin Hauser, Robbin Thorp and Jason
Gibbs.  This work was supported by funding from the Army Research
Office (W911NF-11-1-0361 to CK), the Natural Resources Conservation
Service (CIG-69-3A75-12-253, CIG-69-3A75-9-142, CIG-68-9104-6-101 and
WLF-69-7482-6-277 to The Xerces Society), the National Science
Foundation (DEB-0919128 to CK), The U.S.  Department of Agriculture
(USDA-NIFA 2012-51181-20105 to Michigan State University).  Funding
for LCP was provided by an NSF Graduate Research Fellowship, the USDA
NIFA Graduate Fellowship, and the Berkeley Institute for Data
Science. Funding for MPG was provided by S{\~a}o Paulo Research
Foundation (FAPESP, grant 2013/13319-5). We also appreciate the Santa
Fe Institute for facilitating this international collaboration.

@@

>>>>

\begin{abstract}  
  % The ability of communities to maintain function in the face of
  % species extinction is related to the structure of networks. Lauren
  % - i changed the phrasing because structure of network and network
  % structure were too close.
  The structure of interaction networks is related to the ability of communities to maintain function in the face of
  species extinction. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for conservation
  biology. Using a nine-year-dataset comprising nearly $20,000$
  pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing community assembly to be
  punctuated by major interaction reorganizations.%  In contrast, the
  % non-assembling networks did not restructure as frequently.
  % Across all communities, pollinator species were opportunistic in the
  % flowers they visited.
   Generalist species were the most persistent and 
also the most variable in their network positions, contrary to
  what is expected through prefereantial attachment theory. % High
  % species and interaction turnover was ubiquitous across assembling
  % and non-assembling communities, though unique interactions turned
  % over at higher rates in assembling hedgerows as the networks
  % continually reorganized.
  % Nestedness of assembling networks also increased through time, but
  The sensitivity of networks to cascading perturbations,
  increased with assembly, at least partially due to accumulating
  species richness. We elucidate some of the mechanisms underlying
  plant-pollinator network assembly and restoration --- challenging
  the widely-held hypothesis that mutualistic networks assemble
  through preferential attachment.
\end{abstract}

@@

%% there are other ways to assemble that are not preferentia;
%% attchment, particularly vis big reorganizations of interactions
%% Lauren I love this paragraph!
In contrast to the network build-up described by preferential
attachment, significant reorganizations of interactions can punctuate
assembly \citep{peel2014detecting}. Such significant reorganizations
of interactions, or network changing points, are observed in social
networks that respond to abrupt shifts in the behavior of interactors
\citep{peel2014detecting}. In ecolo% gical communities, such shifts may
% occur if, as new species colonize, resident species change their
% interaction partners to optimize their foraging effort. In
% plant-pollinator communities, theory predicts that pollinators
% optimize their use of floral resources to reduce interspecific
% competition and improve resource-use efficiency
% \citep{pyke1984optimal, valdovinos2010consequences,
%   valdovinos2013adaptive, albrecht2010plant, Bluthgen2007}. No
% studies, however, have examined whether network changing points occur
% during ecological network assembly, and how these changes relate to
% the species behavior.

% %% restoration
% Understanding network assembly is particularly relevant to ecological
% restoration, which is essentially ``applied succession''
% \citep[e.g.,][]{parker1997scale}. In pollination systems, the time
% since an area was restored has been shown to affect the structure of
% networks \citep{forup-2008-742, devoto2012understanding}, suggesting
% interactions are changing as the community develops. Understanding the
% mechanisms of network assembly will help to guide community
% restoration. Facilitating network restoration is especially imperative
% in areas where species interactions provide essential ecosystem
% services, such as crop pollination. To ensure the continued provision
% of ecosystem services and curb biodiversity loss, it is critical to
% restore pollinators and their interactions in agricultural
% landscapes. To promote pollinator services in agriculture, farmers may
% chose to plant strips of native plants along farm edges (hedgerows) to
% help provide habitat for pollinators without removing arable land from
% production. Hedgerows augment the richness, abundance and trait
% diversity of pollinators in agricultural landscapes
% \citep{morandin-2013-829, kremen-2015-602, ponisio2015farm}, and
% promote the persistence and colonization of floral resource
% specialists \citep{mgonigle-2015-x}. It is important to understand how
% these new species are being incorporated into the network as the
% community assembles, and the consequences for interaction patterns and
% robustness.

% %% Lauren I would put 10 year dataset; and I *loved* the way you
% %% organized the ideas here!!
% We explore the process of network development using a nine year
% dataset of plant-pollinator community assembly following hedgerow
% restoration in the highly simplified and intensively managed
% agricultural landscape of California's Central Valley.  We first
% determine whether the mechanism underlying network assembly is a build
% up of interactions as would be predicted by preferential attachment,
% or instead is punctuated by significant reorganizations of
% interactions (i.e., network changing points). Even with changing
% points in interaction organization, networks could still be assembling
% via preferential attachment if the network reorganizations were
% primarily driven by peripheral, temporally variable species while a
% stable, well-connected core of species persist. We test whether the
% species that are most variable in their network position --- and thus
% important contributors to network reorganizations --- are less
% persistent and connected species. To further explore the mechanisms
% underlying the temporal dynamics of the networks, we examine patterns
% in the species and interaction temporal turnover. Lastly, we
% investigate whether networks are assembling toward predictable
% interaction patterns, and the ramifications for the robustness of the
% networks to species extinction and cascading perturbations.

% %% objectives
% % 1) Are hedgerows assembling by preferential attachment, or are there
% % more abrupt reorganizations of network structure?
% % 2) Who are the species responsible for interaction reorganizations?
% % how to incorporate this? 
% % 3) Are the changing points a product of turnover in species
% % composition, or are more substantial changes in the verticles of the
% % networks?
% % 4) Is the structure of interactions changing? Does this change the
% % robustness of the network to species extinction and/or perturbation?

% \section*{Materials \& Methods}
% \label{sec:methods}

% \subsection*{Study sites and collection methods}
% \label{sec:study-sites}

% We surveyed plant-pollinator interaction networks of independent
% assembling hedgerows communities (N=5), and of two types of
% non-assembling communities to serve as controls: unrestored, weedy
% field margins (N=19) and mature hedgerows (greater than 10 years since
% planting, N=29). The sites were located in the Central Valley of
% California in Yolo, Colusa and Solano Counties. This area is composed
% of intensively managed agriculture --- primarily monocultures of
% conventional row crops, vineyards and orchards. Hedgerows are ca.~3--6
% m wide and approximately 350 m long, bordering large (ca.\
% 30--hectare) crop fields. Hedgerows consist of native, perennial,
% shrub and tree plantings including \textit{Rosa californica},
% \textit{Cercis occidentalis}, \textit{Ceanothus spp.},
% \textit{Heteromeles arbutifolia}, \textit{Sambucus mexicana},
% \textit{Eriogonum spp.}, \textit{Baccharis spp.}, \textit{Salvia
%   spp}. and others \citep[Fig.~S1, ][]{menz-2010-4, kremen-2015-602,
%   mgonigle-2015-x}. The mean distance between monitoring sites was
% $15$ km, and the minimum distance between sites sampled in the same
% year was 1 km.  The entire area surveyed spanned almost $300$
% km$^2$. The crop fields adjacent to all sites were similarly managed
% as intensive, high-input monoculture.

% Monitoring of assembling hedgerows began in 2006 and continued through
% 2014. Surveys of these sites began the year before the area was
% restored. For logistical reasons, no sampling of assembling hedgerows
% was conducted in 2010. Sites were sampled between two and five times
% per year (Tables S1-S3, mean $3.4$ samples per year). In each round of
% sampling, the order in which sites were sampled was
% randomized. Surveys were conducted under sunny conditions when the
% temperature was above $21^{\circ}\mathrm{C}$ and wind speed was below
% $2.5$ meters/second.

% Flower-visitors to plants in hedgerows and unrestored controls were
% netted for one hour of active search time (the timer was paused when
% handling specimens). Honeybees (\textit{Apis mellifera}) were not
% collected because their abundance is determined largely by hive
% placement by bee-keepers. All other insect flower visitors that
% touched the reproductive parts of the flower were collected; however,
% here we focus only on wild bees and syrphids --- the most abundant and
% effective pollinators in the system (representing 49 and 19 percent of
% records, respectively, C.~Kremen, A.~Klein and L.~Morandin,
% unpublished data). Bee and syrphid specimens were identified to
% species (or morpho-species for some bee specimens in the genera
% \textit{Nomada} and \textit{Sphecodes}) by expert taxonomists.

% Quantitative networks were generated for each site through time. To
% account for the unequal number of surveys between years (Tables
% S1-S3), we use the mean of the interactions between a pair of plants
% and pollinators across surveys within a year to represent interaction
% frequency.

% \subsection*{Change point analysis}
% \subsubsection*{Identifying change points}
% We employed a change point detection method \citep{peel2014detecting}
% to identify fundamental reorganizations in large-scale interaction
% patterns. A change point is caused by a merge, split, fragmentation or
% formation of modules (also called compartments). Change point
% detection methods have yet to be generalized to quantitative networks,
% so for this analysis we focused on qualitative (binary)
% networks. Following \cite{peel2014detecting}, we first defined a
% probability distribution over the networks using the generalized
% hierarchical random graph model (GHRG). The GHRG model is able to
% capture both assortative and disassortative structure patterns at all
% scales in the network \citep{peel2014detecting}. A network $G$ is
% composed of vertices $V$ and edges $E$. The GHRG model decomposes the
% $N$ vertices into a series of nested groups, the relationships among
% which are represented by the dendrogram $T$. The tips of $T$ are the
% vertices of $G$, and the probability that two vertices $u$ and $v$
% connect is given by the parameter $p_r$. The probability distribution
% of the network $G$ is thus defined as:

% \begin{equation}
%   \label{eq:lik}
%   P(G|T,{pr}) = p_r^{E_r}(1-p_r)^{N_r-E_r}
% \end{equation}
% % 
% Where $E_r$ is the observed number of edges between vertices with the
% common ancestor $r$, and $N_r$ is the total possible edges.

% Using Bayesian posterior inference and techniques from phylogenetic
% tree reconstruction, we fit the GHRG model to the networks
% \citep{peel2014detecting}. This is accomplished by using a Markov
% chain Monte Carlo (MCMC) procedure to first sample the posterior
% distribution of bipartitions, from which a consensus tree is derived
% \citep{peel2014detecting}. We use $\beta$ distributions with the
% hyperparameters $\alpha=\beta=1$ to define priors for $p_r$.

% Once the GHRG model has been fit to the networks, we determine whether
% a change point occurred between two time slices. To detect a change
% point, we use Bayes factors to compare the fit of two models --- one
% where a change point occurred between two networks, and one where no
% change occurred. We chose a sliding window of length, $w$, of four,
% within which to find change points. Larger windows allow for more
% gradual changes, and four was the maximum possible with our eight
% years of data. Lastly, to calculate a $p$-value for the Bayes factors,
% we use parametric bootstrapping to numerically estimate the null
% distribution \citep{peel2014detecting}. We employed code published
% online by L.~Peel for the change point analysis. Analyses were
% conducted in Python 3.4.

% We next test whether the change points occurring in maturing hedgerows
% were a component of the assembly process or a product of environmental
% shifts that lead to network reorganizations in all types of
% communities. We model the number of change points as successes and the
% total number of years each site was sampled as trials, and use a
% generalized linear model with Binomial error to test whether the
% probability of a change point occurring varied by site type
% \citep{lme4}. We used standard techniques to determine whether the
% assumptions of the models were met for this and all subsequent
% models. For the non-assembling hedgerows and weedy field margins, only
% sites with five or greater survey years were included in this analysis
% (N=11). All statistical analyses were conducted in R 3.2.3 \citep{R}.

% \subsubsection*{Characteristics of species that contribute to change
%   points}

% To further elucidate the nature of the change points, we examine the
% characteristics of the species that contributed to interaction
% reorganization. Some species remain in relatively similar network
% positions through time, whereas others are more variable in their
% position and thus contribute more strongly to network
% reorganization. We test whether the more persistent species with the
% highest degree (number of different interaction partners) are the
% most stable in their network positions, as would be expected if the
% networks were assembling via preferential attachment.

% We calculate species persistence as the proportion of surveys in which
% a plant or pollinator is observed. Species observed consistently
% within and between years are thus maximally persistent. Weighted
% species degree is calculated from interaction observations from an
% extensive dataset from Yolo County (approx.~18000 interaction records)
% that included both the data included in this study and additional data
% from sites where we collected flower visitors using the same methods
% \citep{mgonigle-2015-x, ponisio2015farm}. To represent network
% position variability, we computed the coefficient of variation of
% weighted closeness centrality \citep{freeman1978centrality} at each
% site through time. Closeness centrality represents the importance of a
% space by calcuating the path lengths to other vertices (species) in
% the network \citep{freeman1978centrality}. The shorter the mean path
% length to other species, the higher the closeness centrality. We use
% linear mixed models to test whether the species closeness variability
% (log) is related to the persistence or degree of that species
% \citep{lme4, lmetest}. We included random effects for species and
% site. Because the degree and persistence of pollinators were strongly
% correlated, ($\rho = 0.071$, $p$-value $<$ $2*10^{-16}$), we include
% each explanatory variable in separate models. Plant degree and
% persistence were not significantly correlated, but we use the same
% models as we did for the pollinators for consistency.  Because an
% approximately logarithmic increase in closeness centrality, as would
% be expected with assembly by preferential attachment, would also lead
% to high variability in closeness scores, we also test whether log
% closeness centrality increases through time.

% \subsection*{Species and interaction turnover}

% %%Lauren I really liked the way you explained this part =]
% Reorganizations of network structure can be the result of species
% turnover or species changing their interaction partners (i.e.,
% re-wiring). To better understand the mechanisms underlying the
% temporal dynamics of the assembling networks, we examined patterns of
% species and interaction turnover. For example, assembling networks may
% have higher rates of pollinator turnover than non-assembling
% communities because new pollinator species are colonizing and
% establishing themselves \citep{mgonigle-2015-x}. Similarly, because
% species are turning over and pollinators are trying to maximize their
% foraging efficiency based on the species present, interactions may
% turnover more quickly than in established communities. In addition, at
% assembling hedgerows, plants that are unvisited in early years may
% appear to ``colonize'' the networks as they became more attractive
% resources and establish new interactions with pollinators.

@@

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, occupying the same network position and interacting with
similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species
(Fig.~\ref{fig:methods}). We develop a method to examine the temporal
turnover of interactions with weightings based on their similarity. We
followed the algorithm of \cite{ahn2010link} to cluster all the
interactions (edges) hierarchically across sites and years based on
their similarity, and build a dendrogram. The interaction similarity
is based how may plants and pollinators (vertices) two edges share
\citep{ahn2010link, kalinka2011linkcomm}. The more species edges
shared in common, the shorter the branch length between them on the
dendrogram.  We next calculated the temporal turnover of interactions
weighted by their similarity, as approximated by ``phylogenetic''
distance \citep{graham2008phylogenetic, picante-2010-1463}. We then
use linear mixed models to test whether the weighted turnover of
interactions varied between assembling and non-assembling networks,
including site as a random effect \citep{lme4, lmetest}.

@@

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
%Network nestedness significantly increased with assembly
%(Fig.~\ref{fig:baci}, estimate of the slope of nestedness through time
%$\pm$ SE, $1.834 \pm 0.6142$, $p$-value=$0.022$). 
Nestedness and modularity did not change in any predictable pattern
with assembly (Fig.~\ref{fig:baci}). All of the networks were
significantly nested ($z$-scores $>$ $1.96$), but not modular ($z$-scores
$<$ 2, Fig.~\ref{fig:baci}).

@@

\subsection*{Network robustness}
Assembly did not affect network robustness to species
extinction when species were removed incrementally by
degree or abundance % (estimate
% of the slope of robustness through time $\pm$ SE, $6*10^{-5} \pm
% 4*10^{-3}$, $p$-value=$0.987$) ($0.001 \pm 0.003$,
% $p$-value=$0.65$)
In contrast, the sensitivity of networks to cascading perturbations,
as measured by the algebraic connectivity of the network, increased as
the network assembled (Fig.~\ref{fig:rob}, estimate of the slope of
sensitivity to cascading perturbations through time $\pm$ SE, $0.6814
\pm 0.272$, $p$-value=$0.042$).

@@

We would like to thank Paulo R.~Guimar{\~a}es Jr., Aaron Clauset,
Matthew Hutchinson, Rebecca Brunner, and Ana Paula A. Assis for their
invaluable discussions and comments, and Leto Peel for help with the
change point analysis.  We thank the growers and land owners that
allowed us to work on their property. We also greatly appreciate the
identification assistance of expert taxonomists Martin Hauser, Robbin
Thorp and Jason Gibbs.  This work was supported by funding from the
Army Research Office (W911NF-11-1-0361 to CK), the Natural Resources
Conservation Service (CIG-69-3A75-12-253, CIG-69-3A75-9-142,
CIG-68-9104-6-101 and WLF-69-7482-6-277 to The Xerces Society), the
National Science Foundation (DEB-0919128 to CK), The U.S.  Department
of Agriculture (USDA-NIFA 2012-51181-20105 to Michigan State
University).  Funding for LCP was provided by an NSF Graduate Research
Fellowship, the USDA NIFA Graduate Fellowship, and the Berkeley
Institute for Data Science. Funding for MPG was provided by S{\~a}o
Paulo Research Foundation (FAPESP, grant 2013/13319-5). We also
appreciate the Santa Fe Institute for facilitating this international
collaboration.

@@

\clearpage
\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{figures/scheme.pdf}
  \caption{Diagram illustrating the analysis to examine the temporal
    turnover of interactions weighted based on their similarity. A, B
    and C are animal species, and Ps are plant species. The dendrogram
    depicts the interaction similarity across years based on the
    number of shared constituent species.}
  \label{fig:methods}
\end{figure}
\clearpage
